---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# peruGradosAcademicos

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/peruGradosAcademicos)](https://CRAN.R-project.org/package=peruGradosAcademicos)
<!-- badges: end -->

The goal of peruGradosAcademicos is to have an easy way to access degree information from SUNEDU Perú.

## Installation

You can install the development version of peruGradosAcademicos like so:

``` r
remotes::install_github("calderonsamuel/peruGradosAcademicos")
```

## Example

These are basic examples which shows you how to solve common problems:

You want to know the degrees obtained by a particular person:

```{r example}
library(peruGradosAcademicos)

get_constancia(n_dni = "08192557") |> # this gets JSON
    parse_constancia() |> # this parses JSON into clean data.frame
    subset(select = c(nombre, apepat, apemat, gradTitu))
```

You can also do this by specifying the full name of the person (DNI is faster, tho):

```{r}
get_constancia(nombre = "ZEGARRA ROJAS OSWALDO DELFIN") |> 
    parse_constancia() |> 
    subset(select = c(nombre, apepat, apemat, gradTitu))
```

You can also get the highest degree of the specified person's DNI in a single line (without degree metadata):

```{r}
get_mayor_grado_from_dni(n_dni = "08192557")
```



